WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2013-08-02 ms.tex
Awesome title

\title[Rapid-response Bayesian sky localization]{Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates}
\author{Leo Singer and Larry R. Price}
\address{\acs{LIGO} Laboratory, California Institute of Technology, Pasadena, CA 91125, USA}
\ead{\mailto{leo.singer@ligo.org}, \mailto{larryp@caltech.edu}}

@@

Bayesian parameter estimation has many advantages, including broad generality and the ability to make probabilistically meaningful statements even with very low \ac{SNR} measurements. However, in problems of even modest complexity, the marginalization step burdens the analysis with nasty, many-dimensional, ill-behaved integrals. Almost all modern parameter estimation tactics are variations of \ac{MCMC} integration. Though powerful, \ac{MCMC} is slow and non-deterministic. With the most sophisticated \ac{CBC} parameter estimation codes, it still takes days to process a single event.

>>>>

\title[Rapid-response Bayesian sky localization]{WHOOMP! (There It Is) \\
Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients}
\author{Leo Singer and Larry R. Price}
\address{\acs{LIGO} Laboratory, California Institute of Technology, Pasadena, CA 91125, USA}
\ead{\mailto{leo.singer@ligo.org}, \mailto{larryp@caltech.edu}}

@@

Bayesian parameter estimation has many advantages, including broad generality and the ability to make probabilistically meaningful statements even with very low \ac{SNR} measurements. However, in problems of even modest complexity, the marginalization step burdens the analysis with nasty, many-dimensional, ill-behaved integrals. Almost all modern parameter estimation tactics are variations of \ac{MCMC} integration. Though powerful, \ac{MCMC} is slow and non-deterministic. With the most sophisticated \ac{CBC} parameter estimation codes, it still takes days to process a single event. This delay is undesirable for planning targeted \ac{EM} follow\nobreakdashes-up searches of \ac{LIGO} events.
